\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Clayton Ohmes}}\\
	Atlanta, GA $\cdot$ claytonohmes@gmail.com $\cdot$ 5734271033 $\cdot$ https://github.com/claytonohmes\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Missouri S\&T}\hfill Rolla, MO\\
BS: Electrical Engineering \textbar{} Minor: Automation Engineering \hfill Aug 2016 - Dec 2020\\
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{The Clorox Company} \hfill Atlanta, GA\\
\textit{Senior Controls \& OT Network Engineer} \hfill Mar 2023 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Contributed to OT cybersecurity recovery, restoring application servers and connectivity across sites. Helped design and implement new network infrastructure, including firewalls and VPNs, in response to the incident.
	\item Automated repetitive processes and resolved networking issues using Python scripts.
	\item Created SCADA dashboards and developed PLC code to support production analytics and machine control systems.
	\item Acted as the solution architect for a MES application’s changeover sequence, integrating with PLC systems and enhancing the productivity of operators while reducing their learning curve
\end{itemize}
\textit{Electrical, Instrumentation, and Controls Engineer} \hfill July 2022 - Mar 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Lead Electrical and Controls Engineer for various manufacturing projects around the business. Most notable responsibility is a \$150M+ greenfield facility utilizing a new process to manufacture cat litter.
	\item Standardized Active Directory and security structures across multiple plants, ensuring consistency and security in automation software management.
	\item Built the framework for a comprehensive data historian and analytics platform, which was widely adopted across all departments. Trained site employees on its use, enabling better decision-making and operational insights.
\end{itemize}
\hfill Atlanta, GA\\
\textit{Control System Specialist} \hfill Jan 2021 - July 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Led the controls design and commissioning of a \$46 million wipes production line during the peak of the pandemic, ensuring project completion under challenging conditions.
	\item Implemented a Windows server with automated program change management software, developing processes to track and control changes made by technicians.
	\item Managed a team of 16 maintenance technicians across 4 shifts, coordinating downtime planning and troubleshooting efforts to ensure seamless 24/7 operations.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages:   & Python, Powershell, C++, XML                    \\
	APIs and Configurations: & XML, JSON, HTTP, REST                           \\
	Networking:              & Cisco CLI, IPSec, NAT, VPNs, VLAN Configuration \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Machine Utilization Tracking System}} {\sl XML, Python, PLCs, SCADA} \\
Deployed UDTs (User Defined Types) in PLCs across 7 sites to standardize data collection for a root cause analysis engine. Wrote XML configurations using Python to integrate the data into the analysis system.\\
\vspace*{2mm}
{\textbf{Automated Batch Reciept Storage}} {\sl Python, SCADA, NSSM} \hfill https://github.com/claytonohmes/Copy-Directory\\
Added functionality to the SCADA to automate printing batch receipts to PDF under a standard naming convention. Developed a Windows service with NSSM and Python to automate copying them to the plant\textquotesingle{}s file server, ensuring automatic operation on system reboot.\\
\vspace*{2mm}

\header{Certificates}
\textbf{Automate the Boring Stuff with Python} \hfill Udemy\\
\hfill Nov 2023\\
\vspace*{2mm}
\textbf{Python Zero to Hero} \hfill Udemy\\
\hfill Sep 2024\\
\vspace*{2mm}
\textbf{API and Web Service} \hfill Udemy\\
\hfill Sep 2024\\
\vspace*{2mm}

\ 
\end{document}